Einstein's gravity from an affine model

### 2015-07-23 AffGR-PRD.tex
Extended Sec. NR-limit

%% Additionally, we studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
Albeit the inclusion of matter in a non-metric spacetime is a nonstandard procedure, we used ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions. However, for the simple case of the Einstein--Hilbert action, it is in fact the inverse metric density.}, defined as the variation of the action with respect to the symmetric part of the Ricci tensor~(see Refs.~\cite{Eddington1923math,schrodinger1950space,Poplawski:2012bw}), i.e.,%% \hl{JZ: def. $R_{(\mu\nu)}$}
\begin{equation}
  \label{metric}
  \frac{\delta\ }{\delta R_{(\mu\nu)}} S[\Gamma] \equiv \sqrt{\mathsf{g}} \, \mathsf{g}^{\mu\nu} = \bar{g}^{\mu\nu} ,
\end{equation}
by assuming a matter action that depends on $\bar{g}^{\mu\nu}$.

From the geodesic equations and the linearized action on scalar perturbation, we found that the effective geodesic deviation
\begin{equation}
  \label{NewtonPot}
  \Gamma^i{}_{00} = - \frac{1}{8\pi} \frac{ \partial\mathcal{L}_{\text{Matter}} }{ \partial \bar{g}^{00} } \, \nabla^i \left(\frac{1}{|\vec{x}|}\right),
\end{equation}
is the usual Newtonian force induced by a massive source.

>>>>

%% Additionally, we studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
Albeit the inclusion of matter in a non-metric spacetime is a nonstandard procedure, we assumed that the matter action would depend on the most general $\binom{2}{0}$-type symmetric tensor density, $\mathfrak{g}^{\mu \nu}$, constructed with at most quadratic terms in the available fields. This tensor density coincides with what we call the ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions. However, for the simple case of the Einstein--Hilbert action, it is in fact the inverse metric density.}, defined as the variation of the action with respect to the symmetric part of the Ricci tensor~(see Refs.~\cite{Eddington1923math,schrodinger1950space,Poplawski:2012bw}), i.e.,%% \hl{JZ: def. $R_{(\mu\nu)}$}
\begin{equation}
  \label{metric}
  \frac{\delta\ }{\delta R_{(\mu\nu)}} S[\Gamma] \equiv \sqrt{\mathsf{g}} \, \mathsf{g}^{\mu\nu} = \mathfrak{g}^{\mu\nu}.
\end{equation}
%% by assuming a matter action that depends on $\bar{g}^{\mu\nu}$.

From the geodesic equations and the linearized action on scalar perturbation, we found that only a few terms in the scalar perturbation affect the geodesic equation. The effective geodesic deviation is given by
\begin{equation}
  \label{NewtonPot}
  \Gamma^i{}_{00} = - \frac{1}{8\pi} \frac{ \partial\mathcal{L}_{\text{Matter}} }{ \partial \bar{g}^{00} } \, \nabla^i \left(\frac{1}{|\vec{x}|}\right),
\end{equation}
is the usual Newtonian force induced by a massive source.
